\cvsection{Projects and Research}
\begin{cventries}
  \cventry
    {Audio Processing}
    {Acoustic Scene Classification and Audio Tagging}
    {Roorkee, India}
    {MAY 2017 - ONGOING}
    {
      \begin{cvitems}
        \item {Evaluated Audio Features such as Mel-Spectrogram, Constant Q-Transform, and MFCC to
        understand complementary features.}
        \item{Analyzed various Neural Networks to develop an ensemble model to pass the
        audio features, attaining state-of-the-art results.}
      \end{cvitems}
    }
  \cventry
    {\href{http://dit.channelcs.com}{http://dit.channelcs.com}}
    {Paperless Placements Portal}
    {Dehradun, India}
    {AUGUST 2016 - NOVEMBER 2017}
    {
      \begin{cvitems}
        \item {Formulated a portal to handle placement drives of University using PHP and MySql to manage functionality among tables.}
        \item {Placement co-ordinator adds company visits, students mark attendance and manage internships.}
      \end{cvitems}
    }
  \cventry
    {Natural Language Processing}
    {Answer Generation for Machine Reading Comprehension}
    {Roorkee, India}
    {JANUARY 2018 - ONGOING}
    {
      \begin{cvitems}
        \item {An approach to answer the questions from multiple passages.}
        \item {Developing a framework to synthesize answers from extraction results.}
        \item {Building Answer Extraction model for reading comprehension.}
      \end{cvitems}
    }
  \cventry
    {Audio Processing}
    {Logan}
    {Roorkee, India}
    {AUGUST 2016 - APRIL 2017}
    {
      \begin{cvitems}
        \item {Extracted MFCC features on raw audio samples which were passed to Gaussian Mixture Models for speaker identification.}
      \end{cvitems}
    }
  \cventry 
    {Web Application}
    {Handwritten Digit Recognition}
    {Roorkee, India}
    {NOVEMBER 2017 - JANUARY 2018}
    {
    \begin{cvitems}
        \item {An interactive Digital Drawing Space for user to draw digits.}
        \item {Used flask to deploy our prediction algorithm using the weights to predict the Image drawn by the user.}
      \end{cvitems}
    }
\end{cventries}
